---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"#,
  #out.width = "100%"
)
```
# textme

<!-- badges: start -->
<!-- badges: end -->

The heart of this package is a single function called `textme()` that sends you a text message 📱 the instant a long-running job completes. 

This allows you to leave your computer while running code, and know exactly when to return 🎉.  

![](https://pbs.twimg.com/media/EEO4ugSUcAA_x2C?format=jpg&name=900x900)

## Installation

<!-- You can install the released version of textme from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("textme") -->
<!-- ``` -->

Install the development version from github:

```r
devtools::install_github("richpauloo/textme")
```

## Example

First, sign up for a [free Twilio trial account](https://www.twilio.com/). 

Then, provide information about your twilio account and the number you want to text.  

```{r setup, eval = FALSE}
library(textme)

# replace the values here with your own
tm_configure(twilio_sid   = "AC1ffb4919a0f0720787954c0214bde131",
             twilio_token = "f5c8daf3e8904b9af81dda09f975c369",
             twilio_phone_number = "1234567890",
             target_phone_number = "0987654321")
```

The above code needs to be run only once. Now, and in future R sessions, simply run the following to text yourself.   

```{r eval = FALSE}
textme()
```

You can supply a custom message with the `message` argument: 

```{r, eval = FALSE}
textme(message = "Back to work! You're not paid to run around and drink coffee all day!")
```

