---
title: "Send text message notifications from R"
author: "Rich Pauloo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Some R users run code that takes a long time to process. To notify users when code is done execuing, the [`beepr`](https://cran.r-project.org/web/packages/beepr/index.html) package is a great tool that plays a sound on the computer.  

In the spirit of `beepr::beep()`, this package provides a single function called `textme()` that sends you a text message the instant a long-running job completes. This allows you to leave your computer while running code, and know exactly when to return.  

***

This package relies on Twilio to send text messages. Presently, free trial accounts are avaialble. Sign up for a [twilio account here](https://www.twilio.com/).  

On the user dashboard, take note of three pieces of information:  

* Twilio SID  
* Twilio token
* Twilio phone number  

You only need to set these variables once. Afterward, they are stored in the `.Renviron` file of your home directory. To store these variables, use `tm_configure()`. It is recommended that you set a target phone number as well--this should be **your phone number**, where you want to **receive** text messages.    

```{r setup, eval = FALSE}
library(textme)

# replace the values here with your own
tm_configure(twilio_sid   = "AC1ffb4919a0f0720787954c0214bde131",
             twilio_token = "f5c8daf3e8904b9af81dda09f975c369",
             twilio_phone_number = "1234567890",
             target_phone_number = "0987654321")
```

Once you've configured your environment, you should be able to send a text message. In future sessions, you don't need to re-configure anything. You should be able to simply run `textme()` and `R` will load your stored SID, token, and phone numbers.  

```{r eval = FALSE}
textme()
```

To send a custom message, simply supply a `message` argument:
```{r, eval = FALSE}
textme(message = "My custom message.")
```

To send a message to another number, supply a new `target_phone_number`: 
```{r, eval = FALSE}
textme(target_phone_number = "1112223333")
```







